---
title: "Process the CRS data set"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Read data

Assumptions: 

* Basic reporting
* To aim at level 1 and 2, less emphasis on code modularity (i.e. user defined functions) 
* Code to be simple, readable, extendable. 



TODO:add variable to indicate measurement type:

* med history 
* outcome
* Add additional metadata on measurement schedule

## Set up

Set up packages and path to the data set. 

```{r setupR}
library(rmarkdown)
library(ggplot2)
library(dplyr)
library(tidyr)
library(Hmisc)
library(here)


## Set global ggplot theme
theme_set(theme_light(base_size = 12))

## Relative path to the data set
crs_data_path = here("data", "crs.Rdata")
```

## Read data

Load the CRS dataset.

```{r}
load(crs_data_path)
```


## Check data

Check data contents and complete any misssing information including labels or units. 

display the data set contents. 

```{r}
Hmisc::contents(crs) 
```

Add missing label for BMI. 

```{r}
crs <- crs %>%
  Hmisc::upData(labels = c(bmi = 'body mass index'))
```


# Descriptive summary

Univariate analyses. 

## Medical history

A summary of medical history measured at *diagnosis* (TODO: check when medical history / comorbidities were assessed):
* AFib, 
* MI
* CHF
* Diabetes 

Print out descriptive summary. 

```{r}
crs %>% 
  select(chf, afib, mi, diabetes) %>%
  Hmisc::describe()
```

Plot of the distribution of patients with specific comorbidities measured at diagnosis. 

Process steps:
* Select comorbidities
* Transform data frame from wide to long
* Transform and spell out factors for plotting
* Plot counts by comorbidity 

```{r}
crs %>%
  select(id, chf, afib, diabetes, mi) %>%
  pivot_longer(-id, names_to = "comorb", values_to = "value") %>%
  mutate(
    comorb = case_when(
      comorb == "chf" ~ "Congestive heart failure",
      comorb == "afib" ~ "Atrial fibrillation",
      comorb == "diabetes" ~ "Diabetes",
      comorb == "mi" ~ "Myocardial infarction"
    ),
    value = case_when(
      value == "0" ~ "no",
      value == "1" ~ "yes")
  ) %>%
  group_by(comorb, value) %>%
  summarise(n = n()) %>%
  ggplot(aes(value, n)) +
  geom_col(width = 0.6, alpha = 0.15, fill = "red") +
  geom_text(aes(y=n, label = n), nudge_y = 1.5) +
  coord_flip() +
  facet_wrap(~ comorb) + 
  ylab("Number of patients") +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank()
  )

```




## Patient characteristics 

TODO


# Bivariate data display

TODO
