---
title: "Process the CRS data set"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Set up

Assumptions: 

* Basic reporting
* Code is simple, readable. 
* Less emphasis on modularity (i.e. functions) to aim at level 1 and 2


TODO: add variable to indicate measurement type:
* MH
* cormodoities
* outcome
Add additional metadata on measurement timing

Set up packages and path to the data set. 

```{r setupR}
library(rmarkdown)
library(ggplot2)
library(dplyr)
library(Hmisc)
library(here)
library(patchwork)

## Relative path to the data set
crs_data_path = here("data", "crs.Rdata")
```

## Read data

Load the CRS dataset.

```{r}
load(crs_data_path)
```


# Univariate data display

## Medical history

## Patient characteristics 

```{r}
gg1 <- crs %>%
  ggplot(aes(y = bmi)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw()
```


```{r}
gg1 + gg1 + gg1 
```


# Bivariate data display
