---
title: "Univariate summaries"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setupR}
library(rmarkdown)
library(ggplot2)
library(dplyr)
library(tidyr)
library(Hmisc)
library(here)

## Set global ggplot theme
theme_set(theme_light(base_size = 12))
```

## Read data

Load the CRS dataset.

```{r}
load(here("data","a_crs.Rdata"))
```


# Descriptive summary

Univariate analyses. 

Calculate the number of patients.

```{r}
bigN <- nrow(crs)
print(bigN)
```

## Medical history

A summary of medical history measured at *diagnosis* (TODO: check when medical history / comorbidities were assessed):
* AFib, 
* MI
* CHF
* Diabetes 

Print out descriptive summary. 

```{r}
crs %>% 
  select(chf, afib, mi, diabetes) %>%
  Hmisc::describe()
```

Plot of the distribution of patients with specific comorbidities measured at diagnosis. 

Process steps:
* Select comorbidities
* Transform data frame from wide to long
* Transform and spell out factors for plotting
* Plot counts by comorbidity 

```{r}
crs %>%
  select(id, chf, afib, diabetes, mi, copd) %>%
  pivot_longer(-id, names_to = "comorb", values_to = "value") %>%
  mutate(
    comorb = case_when(
      comorb == "chf" ~ "Congestive heart failure",
      comorb == "afib" ~ "Atrial fibrillation",
      comorb == "diabetes" ~ "Diabetes",
      comorb == "copd" ~ "COPD",
      comorb == "mi" ~ "Myocardial infarction"
    ),
    value = case_when(value == "0" ~ "no",
                      value == "1" ~ "yes")
  ) %>%
  group_by(comorb, value) %>%
  summarise(n = n()) %>%
  mutate(
    inc = n / bigN,
    perc = n / bigN * 100,
    plot_lab = paste0('(', n, ', ', round(perc, digits = 1), '%)')
  ) %>%
  ggplot(aes(value, n)) +
  geom_col(width = 0.6,
           alpha = 0.15,
           fill = "red") +
  geom_text(aes(y = n, label = plot_lab), size = 3.5, nudge_y = 20) +
  scale_y_continuous(limits = c(0, 400)) +
  coord_flip() +
  facet_wrap( ~ comorb, ncol = 2) +
  ggtitle("Number (and percentage) of patients\n reporting comorbidity at diagnosis") +
  ylab("Number of patients") +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank()
  )
```


Alternative way to plot information.

```{r}
crs %>%
  select(id, chf, afib, diabetes, mi, copd) %>%
  pivot_longer(-id, names_to = "comorb", values_to = "value") %>%
  mutate(
    comorb = case_when(
      comorb == "chf" ~ "Congestive heart failure",
      comorb == "afib" ~ "Atrial fibrillation",
      comorb == "diabetes" ~ "Diabetes",
      comorb == "copd" ~ "COPD",
      comorb == "mi" ~ "Myocardial infarction"
    ),
    value = case_when(value == "0" ~ "no",
                      value == "1" ~ "yes")
  ) %>%
  group_by(comorb, value) %>%
  summarise(n = n()) %>%
  mutate(
    inc = n / bigN,
    perc = n / bigN * 100,
    plot_lab = paste0('(', n, ', ', round(perc, digits = 1), '%)'),
    axis_lab = paste0(value, ' ','(', n, ', ', round(perc, digits = 1), '%)')
  ) %>%
  ggplot(aes(axis_lab, n)) +
  geom_col(width = 0.6,
           alpha = 0.15,
           fill = "red") +
  coord_flip() +
  facet_wrap( ~ comorb, ncol = 1, scales = "free_y") +
    ggtitle("Number and percentage of patients reporting\n a comorbidity at diagnosis") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.title = element_blank()
  )
```


## Patient characteristics 

TODO

# Session info

```{r}
sessionInfo()
```

